### 2015-05-11 papers/histogram/thesis/poster.tex
updates to poster

    \begin{figure}[H]
      \centering
      \includegraphics[width=0.5\columnwidth]{figs/dos-example.pdf}
      \caption{Sample density of states of a particular square-well
        fluid ($\lambda=1.3$, $\eta=0.3$), as computed using several
        methods. The logarithmic span of the density of states is
        proportional to the number of moves one must simulate via
        standard Monte Carlo in order to observe the energies with the
        lowest state densities.}
      \label{fig:dos}
    \end{figure}

@@

    % There are various published histogram methods, but little to no
    % literature exists on these methods' systematic comparison, or on
    % their application to the square-well fluid. We implement several
    % methods, including Wang-Landau, transition matrix Monte Carlo, and
    % a modified version of the so-called optimized ensemble, and
    % determine several metrics for their comparison.

    \begin{itemize}
    \item Means for biasing Monte Carlo simulations in favor of lower
      energy states
    \item Accept all moves in simulation which lower the system's
      energy, probabilistically reject moves to higher energy
    \item Details of rejection process define a histogram method
    \item There are several published histogram methods, but little to
      no literature on their systematic comparison, or their
      application to the square-well fluid
    \item We implement several methods: our own ``simple flat''
      method, Wang-Landau, transition matrix Monte Carlo (TMMC), and a
      hybrid of TMMC with a so-called ``optimized ensemble'' method
    \end{itemize}

@@

  \headerbox{Comparison}
  {name=comparison,column=2}{%

    \begin{figure}[H]
      \centering
      \includegraphics[width=0.5\columnwidth]{figs/sample-rates.pdf}
      \caption{Sample rates}
      \label{fig:sample_rates}
    \end{figure}
    \begin{figure}[H]
      \centering
      \includegraphics[width=0.5\columnwidth]{figs/u-comps.pdf}
      \caption{Errors}
      \label{fig:errors}
    \end{figure}

@@

  \headerbox{Conclusions}
  {name=conclusions,column=2,below=comparison}{%

>>>>

    \begin{figure}[H]
      \centering
      \includegraphics[width=0.5\columnwidth]{figs/dos-example.pdf}
      \caption{Sample density of states of a particular square-well
        fluid ($\lambda=1.3$, $\eta=0.3$). The logarithmic span of the
        density of states is proportional to the number of moves one
        must simulate via standard Monte Carlo in order to observe the
        energies with the lowest state densities.}
      \label{fig:dos}
    \end{figure}

@@

    % There are various published histogram methods, but little to no
    % literature exists on these methods' systematic comparison, or on
    % their application to the square-well fluid. We implement several
    % methods, including Wang-Landau, transition matrix Monte Carlo, and
    % a modified version of the so-called optimized ensemble. We compare
    % low energy sampling rates for all methods, as well as relative
    % errors in thermodynamic properties computed via each method.

    \begin{itemize}
    \item Means for biasing Monte Carlo simulations in favor of lower
      energy states
    \item Accept all moves in simulation which lower the system's
      energy, probabilistically reject moves to higher energy
    \item Details of rejection process define a histogram method
    \item There are several published histogram methods, but little to
      no literature on their systematic comparison, or their
      application to the square-well fluid
    \item We implement several methods: our own ``simple flat''
      method, Wang-Landau, transition matrix Monte Carlo (TMMC), and a
      hybrid of TMMC with a so-called ``optimized ensemble'' method
    \item Comparison metrics: low energy sampling rates, and relative
      errors in thermodynamic properties computed using results from
      simulating via each method
    \end{itemize}

@@

  \headerbox{Results}
  {name=results,column=2}{%

    \begin{figure}[H]
      \centering
      \includegraphics[width=0.6\columnwidth]{figs/sample-rates.pdf}
      \caption{Iterations per statistically independent energy
        sample.}
      \label{fig:sample_rates}
    \end{figure}
    \begin{figure}[H]
      \centering
      \includegraphics[width=0.6\columnwidth]{figs/u-comps.pdf}
      \caption{Maximum errors in a set of simulations, relative to a
        method which controls for system size and simulation time.}
      \label{fig:errors}
    \end{figure}

@@

  \headerbox{Conclusions}
  {name=conclusions,column=2,below=results}{%
